An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-06-16 gas-adsorption/referee-response.md

## Response to referees

Dear editor,

The responses of referees 1 and 3 could hardly be more divergent.  Our work is impactful precisely because it can tell researchers when to stop looking... or perhaps more relevantly it can tell funding agencies when to stop funding research in this direction.  This is threatening, and Referee 1 doesn't seem interested in knowing whether we should stop looking at porous materials for natural gas and hydrogen storage.

@@

The referee gives a litany of structural properties that we do not address in
our model: "pore volume, pore size, specific surface area, crystal density,
skeletal density, packing density, different adsorption sites etc."

    We note that some of these (e.g. crystal density, skeletal density)
    manifestly have no impact on the property we are studying, which is
    volumetric storage capacity.  Others of course do impact the volumetric
    storage capacity of a material, but do not relate to an upper bound
    specifically.  TODO: We do add a discussion of the pore volume fraction
    and how it can constrained by our upper bound, to make more clear the
    range of applications of our bound.  TODO: We can put a lower bound on
    pore volume fraction contingent on the maximum density having a given value.
    It will take some explanation, but I think is worthwhile.

The other suggestion of Referee 1 is that we clearly state the capacity that we report, as discussed by Parilla et al.

   The deliverable capacity is defined in the paper as "the density of the gas
   in the material at the storage pressure p_full minus the residual gas that
   remains adsorbed at the lowest pressure p_empty such that sufficient flow is
   maintained to feed the engine."  We believe this is clear. The various
   capacities of Parilla et al. are geared towards experimental measurements and
   account for experimental uncertainty in the volume of material, an issue
   which is not present in a theoretical paper.  We note that the paper Referee 1 brought up as an example does not any more clearly define "usable capacity" as they refer to what we call "deliverable capacity".  They do cite Parilla et al., but only in the context of describing their experimental equipment.

### 2021-06-16 gas-adsorption/rsc-gas-ads-complete.tex
nicer name for beginning and ending edit section
add label to changebar, and use macros that maybe mean more than cbstart and cbend?
small changes in response to referees

\usepackage[color]{changebar}
\cbcolor{red}

@@

For a vehicle employing a porous material to store natural gas or hydrogen, the
(volumetric) \emph{deliverable capacity} of the gas is the primary
thermodynamic property that determines the driving
range on a given ``full'' tank of fuel~\cite{mason2014evaluating}. 
The adsorbed gas storage tank delivers the
gaseous fuel to the engine via an (assumed) isothermal pressure
swing~\cite{sircar2002pressure}. The deliverable capacity (see
Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage
pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest
pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set
deliverable capacity targets for both adsorbed methane and hydrogen storage and
delivery for vehicles. For methane, the Advanced Research Projects
Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$
per L of adsorbent at 298 K using a 65\,bar to 5.8\,bar pressure
swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of
progressive targets at five year intervals, with the ultimate target of 0.05\,kg
H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a
minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the
emergence of highly tunable materials with large surface areas, such as
metal-organic frameworks~\cite{furukawa2013chemistry} and covalent organic 
frameworks~\cite{diercks2017atom}, no porous material has met these deliverable capacity targets.

@@

\cbstart
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{figs/two-phase}
    \caption{Cartoon of a two-phase, collapsing material. The material can exist in two phases: an open phase in which gas molecules can adsorb and a closed phase that is collapsed and cannot fit any gas molecules. Take the closed phase as more stable, so that the material can collapse and expels residual gas.
    The pressure of gas at which the structural transition occurs depends on the gas-host interactions and relative stability of the phases. We wish for the structural transition to occur between $\pfull$ and $\pempty$.
    }
    \label{fig:flexible-cartoon}
\end{figure}

@@

\cbend

>>>>

\usepackage[color]{changebar}
\cbcolor{red}
\newcommand\startreferees[1]{\cbstart \noindent\textit{\color{red}%
[\textbf{To referees:} #1]}

}
\newcommand\donereferees{\cbend}

@@

\startreferees{Deliverable capacity defined below}
For a vehicle employing a porous material to store natural gas or hydrogen, the
(volumetric) \emph{deliverable capacity} of the gas is the primary
thermodynamic property that determines the driving
range on a given ``full'' tank of fuel~\cite{mason2014evaluating}. 
The adsorbed gas storage tank delivers the
gaseous fuel to the engine via an (assumed) isothermal pressure
swing~\cite{sircar2002pressure}. The deliverable capacity (see
Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage
pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest
pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set
deliverable capacity targets for both adsorbed methane and hydrogen storage and
delivery for vehicles. For methane, the Advanced Research Projects
Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$
per L of adsorbent at 298 K using a 65\,bar to 5.8\,bar pressure
swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of
progressive targets at five year intervals, with the ultimate target of 0.05\,kg
H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a
minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the
emergence of highly tunable materials with large surface areas, such as
metal-organic frameworks~\cite{furukawa2013chemistry} and covalent organic 
frameworks~\cite{diercks2017atom}, no porous material has met these deliverable capacity targets.

\donereferees

@@

\startreferees{Flexible MOFs section added below}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{figs/two-phase}
    \caption{Cartoon of a two-phase, collapsing material. The material can exist in two phases: an open phase in which gas molecules can adsorb and a closed phase that is collapsed and cannot fit any gas molecules. Take the closed phase as more stable, so that the material can collapse and expels residual gas.
    The pressure of gas at which the structural transition occurs depends on the gas-host interactions and relative stability of the phases. We wish for the structural transition to occur between $\pfull$ and $\pempty$.
    }
    \label{fig:flexible-cartoon}
\end{figure}

@@

\donereferees
